---
  title: "Week 1 Assingment"
author: "Pratistha Khadga"
date: "September 5, 2019"
output: 
word_document: default
html: default
---
  ```
#PRATISTHA KHADGA

# Assignment 1 using knn to determine the species of a new iris

## To make sure all the required packages are installed I have again installed the required packages 
```
```{r}
install.packages("rmarkdown")
install.packages("ggplot2")
install.packages("DescTools")
```
## To make uses of the required packages we use the library command to bring forth all the packages
```{r}
library(ggplot2)
library(class)
library(DescTools)
```
## The assignment requires only the uses of Peatal Length and Petal Width and Speices of the iris flowers 
## Therefore we create a new data with only the required parameters
```{r}
dfiris4 <- data.frame(iris$Petal.Length, iris$Petal.Width, iris$Species)
```
##Then we assign names to the required parameters
```{r}
names(dfiris4) <- c("Length", "Width", "Species")
```
## The next step is to explore the data (making sure the derived data is what is required)
```{r}
dfiris4