---
title: "Week 1 Assingment"
author: "Pratistha Khadga"
date: "September 5, 2019"
output: 
word_document: default
html: default
---
```
#PRATISTHA KHADGA

# Assignment 1 using knn to determine the species of a new iris

## To make sure all the required packages are installed I have again installed the required packages 
```
```{r}
install.packages("rmarkdown")
install.packages("ggplot2")
install.packages("DescTools")
```
## To make uses of the required packages we use the library command to bring forth all the packages
```{r}
library(ggplot2)
library(class)
library(DescTools)
```
## The assignment requires only the uses of Peatal Length and Petal Width and Speices of the iris flowers 
## Therefore we create a new data with only the required parameters
```{r}
dfiris4 <- data.frame(iris$Petal.Length, iris$Petal.Width, iris$Species)
```
##Then we assign names to the required parameters
```{r}
names(dfiris4) <- c("Length", "Width", "Species")
```
## The next step is to explore the data (making sure the derived data is what is required)
```{r}
dfiris4
```
## To get visual representation of the data we have derived a scatter plot of the data  
```{r}
ggplot(dfiris4, aes(x = Length, y = Width, col = Species)) + geom_point()
```
## Now to begin with the assignment using knn 

## we assign a value to k variable
```{r}
myK <- 3
```
## As a test we give new length and width to a new iris flower
```{r}
myiris <- data.frame("Length"=2.25, "Width"=0.75)
```
## Checking the new iris parameters
```{r}
myiris
```
## TO check which type of 'species' the new flower is most similar to we create a function measuring its distance from other's already exsisting in the data data  
```{r}
euclDist <-function(x,y){
  return(
    sqrt((x-myiris$Length)^2 +(y-myiris$Width)^2))
}
```
## we test this function putting in the values provided for the assignment
```{r}
euclDist(2,1)

euclDist(2.25,0.75)
```

## we create a new colum dist measuring distance, using every lenght and width provided in the data
## this is done by the use of mapply
```{r}
dfiris4$Dist <- mapply(euclDist, x = dfiris4$Length, y = dfiris4$Width)
```
##To enable the use of the variables in our data frame without having to call them we use the attach function
```{r}

attach(dfiris4); dfiris4 <- dfiris4[order(Dist),];

##To enable the use of the Desctool package to perform the  next step we use the detach function

detach(dfiris4)
```
## To see the top 3 rows of the data table with the new coloum we use the following step
```{r}
head(dfiris4, n= myK)
```
##The final output and conclusion determining the species of the new 
```{r}
paste ('The new Iris is classified as belonging to the' , DescTools::Mode(dfiris4[1:myK, 3]),
       'species.' )
```
